---
title: "fantasy soccer experiment"
author: "Daniel Kerstan"
date: "8/29/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(jsonlite)
library(httr)
library(dplyr)
library(tidyverse)
library(combinat)
library(gtools)
library(kableExtra)
```


set up variables
```{r}
spending_limit <- 160

gk_num <- 1
def_num <- 2
mid_num <- 2
fwd_num <- 1

team_total_num = sum(gk_num, def_num, mid_num, fwd_num)

same_club_num <- 3
```

# Rules:
## can only have `r gk_num` gk, `r def_num` def, `r mid_num` mid, and `r fwd_num` fwd
## no more than `r same_club_num` from the same club
## only have $`r spending_limit` to spend


```{r}
df <- tribble(~name, ~points, ~position, ~ club, ~price,
              "A", 45, "gk", "blue", 30,
              "B", 66, "gk", "red", 50, 
              "C", 21, "gk", "yellow", 18,
              "D", 38, "mid", "blue", 24,
              "E", 23, "mid", "red", 17,
              "F", 5, "mid", "yellow", 10,
              "G", 11, "mid", "blue", 10, 
              "H", 30, "mid", "red", 15,
              "I", 55, "def", "yellow", 44,
              "J", 40, "def", "blue", 27,
              "K", 36, "def", "red", 22, 
              "L", 55, "def", "yellow", 47, 
              "M", 0, "fwd", "blue", 5,
              "N", 27, "fwd", "red", 20, 
              "O", 18, "fwd", "yellow", 13, 
              "P", 48, "fwd", "blue", 35, 
              "Q", 60, "mid", "yellow", 48, 
              "R", 41, "gk", "blue", 30, 
              "S", 33, "def", "blue", 17)

df %>% 
  kable() %>% 
  kable_paper(lightable_options = "striped") %>% 
  kable_styling(full_width = FALSE)


```


```{r}
team_bonus_df <- tribble(~club, ~defender_bonus, ~fwd_bonus, ~gk_bonus,
                         "blue", 10, 5, 8,
                         "red", 0, 13, 7,
                         "yellow", 5, 8, 1)

team_bonus_df %>% 
  kable() %>% 
  kable_paper(lightable_options = "striped") %>% 
  kable_styling(full_width = FALSE)
```


# 1
Setting up associations to filter by
```{r}
name_club <- df %>% 
  select(name, club)

name_points <- df %>% 
  select(name, points)

name_price <- df %>% 
  select(name, price)
  
```

full list of combinations based on player name
```{r}
analysis <- as.data.frame(combinations(n = length(df$name), r = team_total_num, v = df$name))

team_seq <- seq(from = 1, to = length(analysis$V1))

analysis <- analysis %>% 
  mutate(team = team_seq)

# all combinations have now been given a team number
```





# 2
second phase: `pivot_longer` and left join player position by name
```{r}
analysis_2 <- pivot_longer(data = analysis, cols = -"team", names_to = "spot", values_to = "name")

```

```{r}
player_position <- df %>% 
  select(name, position)

analysis_3 <- left_join(analysis_2, player_position, "name")
```


```{r, eval=FALSE}
# an interesting visualization of the combinations but not helpful in computation
analysis_3_wider <- pivot_wider(data = analysis_3, id_cols = team, names_from = position, values_from = name)
```
counting how many of each position are on each team
```{r}
analysis_4 <- analysis_3 %>% 
  count(team, position)
```

```{r}
analysis_4_wider <- analysis_4 %>% 
  pivot_wider(team, names_from = position, values_from = n)
```
filter only those that satisfy the position requirements
```{r}
team_sat <- analysis_4_wider %>% 
  filter(gk == gk_num & mid == mid_num & def == def_num & fwd == fwd_num)
```
cutting down the previous list (analysis_3) by the position filter by a left join
```{r}
full_sat <- left_join(team_sat, analysis_3, by = "team")
```

```{r}
full_sat_wider <- pivot_wider(data = full_sat, id_cols = team, names_from = spot, values_from = name)
```
now have a filtered df containing team, spot, name, and position that meets the position requirement
```{r}
full_sat <- full_sat %>% 
  select(team, spot, name, position)
```



# 3
setting up to filter by club to satisfy club player limit
```{r}
full_sat_club <- left_join(full_sat, name_club, by = "name")
```
counting how many players per team per club
```{r}
analysis_5 <- full_sat_club %>% 
  count(team, club)
```

```{r}
analysis_5_wider <- pivot_wider(data = analysis_5, names_from = club, values_from = n)
```
filter only those combinations (teams) that satisfy the club requirements
```{r}
satisfied_almost <- analysis_5_wider %>% 
  filter(blue <= same_club_num & red <= same_club_num & yellow <= same_club_num) %>% 
  select(team)
# 1 column data frame consisting of just team number that satisfies
```
left join to get updated satisfied df of teams
```{r}
satisfied <- left_join(satisfied_almost, full_sat_club, by = "team")
```


# 4
adding price
```{r}
price_considered <- left_join(satisfied, name_price, by = "name")
```
sum the price per team
```{r}
sum_price_team <- price_considered %>% 
  group_by(team) %>% 
  summarize(total_price = sum(price))
```
filter by price limit of $`r spending_limit`
```{r}
price_almost_sat <- sum_price_team %>% 
  filter(total_price <= spending_limit)
```

```{r}
price_sat <- left_join(price_almost_sat, satisfied, by = "team")
```



# 5
adding up the points

```{r}
points_calc <- left_join(price_sat, name_points, by = "name")
```

add the club bonus
```{r}
points_bonus <- left_join(points_calc, team_bonus_df, by = "club") %>% 
  mutate(bonus = case_when(
    position == "gk" ~ (points + gk_bonus),
    position == "def" ~ (points + defender_bonus),
    position == "fwd" ~ (points + fwd_bonus),
    TRUE ~ points
  ))

final_points <- points_bonus %>% 
  select(team, spot, name, position, club, bonus)
```
get the sum of all points per team
```{r}
analysis_final <- final_points %>% 
  group_by(team) %>% 
  summarize(sum = sum(bonus))
```
establish what the max amount is and find team that has it
```{r}
max_points_withbonus <- max(analysis_final$sum)

team_win_final <- analysis_final %>% 
  filter(sum == max_points_withbonus)
```
show the winning roster
```{r}
winning_roster <- left_join(team_win_final, analysis_2, by = "team")

winning_roster <- winning_roster %>% 
  select(name)

winning_roster <- left_join(winning_roster, df)

with_total_price <- left_join(team_win_final, price_almost_sat, by = "team")

```


# winning roster is `r winning_roster$name` with a combined score of `r max_points_withbonus`, and a total cost of $`r with_total_price$total_price`


```{r}
winning_roster %>% 
  kable() %>% 
  kable_paper(lightable_options = "striped") %>% 
  kable_styling(full_width = FALSE)
```


